The guts of the dispRity package

### 2020-05-01 inst/gitbook/06_guts.Rmd
Revert "gitbook updates"
This reverts commit e41ca75f88719d79e031e170e8ef0df6b29f7ff7.

 * `$matrix`: an object of class `matrix`, the full multidimensional space.
 * `$call`: an object of class `list` containing information on the `dispRity` object content.
 * `$subsets`: an object of class `list` containing the subsets of the multidimensional space.
 * `$disparity`: an object of class `list` containing the disparity values.

The `dispRity` object is loosely based on `C` structure objects.
In fact, it is composed of one unique instance of a matrix (the multidimensional space) upon which the metric function is called via "pointers" to only a certain number of elements and/or dimensions of this matrix.
This allows for: (1) faster and easily tractable execution time: the metric functions are called through apply family function and can be parallelised; and (2) a really low memory footprint:  at any time, only one matrix is present in the `R` environment rather than multiple copies of it for each subset.

### `$matrix`
This is the multidimensional space, stored in the `R` environment as a `matrix` object.
It requires row names but not column names.
By default, if the row names are missing, `dispRity` function will arbitrarily generate them in numeric order (i.e. `rownames(matrix) <- 1:nrow(matrix)`).
This element of the `dispRity` object is never modified.

@@

 * `$call$subsets`: a vector of `character` with information on the subsets type (either `"continuous"`, `"discrete"` or `"custom"`) and their eventual model (`"acctran"`, `"deltran"`, `"random"`, `"proximity"`, `"equal.split"`, `"gradual.split"`). This element generated only once via `chrono.subsets()` and `custom.subsets()`.
 * `$call$dimensions`: either a single `numeric` value indicating how many dimensions to use or a vector of `numeric` values indicating which specific dimensions to use. This element is by default the number of columns in `$matrix` but can be modified through `boot.matrix()` or `dispRity()`.
 * `$call$bootstrap`: this is a `list` containing three elements:
    * `[[1]]`: the number of bootstrap replicates (`numeric`)
    * `[[2]]`: the bootstrap method (`character`)
    * `[[3]]`: the rarefaction levels (`numeric` vector)
 * `$call$disparity`: this is a `list` containing one element, `$metric`, that is a `list` containing the different functions passed to the `metric` argument in `dispRity`. These are `call` elements and get modified each time the `dispRity` function is used (the first element is the first metric(s), the second, the second metric(s), etc.).

@@

>>>>

 * `$matrix`: an object of class `list` that contains at least one object of class `matrix`: the full multidimensional space.
 * `$call`: an object of class `list` containing information on the `dispRity` object content.
 * `$subsets`: an object of class `list` containing the subsets of the multidimensional space.
 * `$disparity`: an object of class `list` containing the disparity values.

The `dispRity` object is loosely based on `C` structure objects.
In fact, it is composed of one unique instance of a matrix (the multidimensional space) upon which the metric function is called via "pointers" to only a certain number of elements and/or dimensions of this matrix.
This allows for: (1) faster and easily tractable execution time: the metric functions are called through apply family function and can be parallelised; and (2) a really low memory footprint: at any time, only one matrix (or list of matrices) is present in the `R` environment rather than multiple copies of it for each subset.

### `$matrix`
This is the multidimensional space, stored in the `R` environment as a `list` object containing one or more `matrix` objects.
Each `matrix` requires row names but not column names (optional).
By default, if the row names are missing, `dispRity` function will arbitrarily generate them in numeric order (i.e. `rownames(matrix) <- 1:nrow(matrix)`).
This element of the `dispRity` object is never modified.

@@

 * `$call$subsets`: a vector of `character` with information on the subsets type (either `"continuous"`, `"discrete"` or `"custom"`), their eventual model (`"acctran"`, `"deltran"`, `"random"`, `"proximity"`, `"equal.split"`, `"gradual.split"`) and eventual information about the trees and matrices used through `chrono.subsets`. This element generated only once via `chrono.subsets()` and `custom.subsets()`.
 * `$call$dimensions`: either a single `numeric` value indicating how many dimensions to use or a vector of `numeric` values indicating which specific dimensions to use. This element is by default the number of columns in `$matrix` but can be modified through `boot.matrix()` or `dispRity()`.
 * `$call$bootstrap`: this is a `list` containing three elements:
    * `[[1]]`: the number of bootstrap replicates (`numeric`)
    * `[[2]]`: the bootstrap method (`character`)
    * `[[3]]`: the rarefaction levels (`numeric` vector)
 * `$call$disparity`: this is a `list` containing one element, `$metric`, that is a `list` containing the different functions passed to the `metric` argument in `dispRity`. These are `call` elements and get modified each time the `dispRity` function is used (the first element is the first metric(s), the second, the second metric(s), etc.).

@@

When a probabilistic model was used to select the elements (models that have the `"split"` suffix, e.g. `chrono.subsets(..., model = "gradual.split")`), the `$elements` is a matrix containing a pair of elements of the matrix and a probability for sampling the first element in that list:

```
 disparity$subsets$sub1$elements
      [,1] [,2]       [,3]
 [1,]   73   36 0.01871893
 [2,]   74   37 0.02555876
 [3,]   33   38 0.85679821
```

In this example, you can read the table row by row as: "there is a probability of `0.018` for sampling element `73` and a probability of `0.82` (`1-0.018`) of sampling element `36`".
